graphsim: An R package for simulating gene expression data from graph structures of biological pathways

### 2020-06-04 paper/paper.Rmd
add citations to introduction

>>>>

GeneNetWeaver @Schaffter2011 - benchmarking of gene regulatory network inference methods
Splatter @Zappia2017 - simulated single-cell RNA-Seq data (gamma-poisson)
dyngen @Cannoodt2020 - single-cell multimodal -  Gillespie’s stochastic simulation at single-molecule level
SERGIO @Dibaeinia2019 - single-cell gene expression (noise with poisson)
